### 2021-04-04 Chapter-3/Chapter-3.tex
Updates from Overleaf

>>>>

While recent works have reported lots
of potential side-channel vulnerabilities, most of them are not patched by
developers. For RSA, the latest
OpenSSL only has one leakage site that can leak more than 3 bits while there
are 22 leakage sites according to \tool{}. DES implementation of OpenSSL has
several sensitive leakages, but given the end life status of DES, it is still
unpatched for the worth of engineering effort.
